D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-14 ootavacuous.tex
Demote quasi-volatile parentheses to comma clause
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Declaring objects to be volatile is a way for the programmer to
indicate that the hardware should perform all accesses to these
objects exactly as written in the source code (perhaps because they
represent memory-mapped device registers or DMA buffers rather than
normal memory locations).
In any event, we expect compilers' translations of volatile-object accesses
into machine code to be as close to verbatim as possible.

>>>>

Declaring objects to be volatile is a way for the programmer to
indicate that the hardware should perform all accesses to these
objects exactly as written in the source code, perhaps because they
represent memory-mapped device registers or DMA buffers rather than
normal memory locations.
In any event, we expect compilers' translations of volatile-object accesses
into machine code to be as close to verbatim as possible.
